\documentclass[11pt,man]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\usepackage{tikz}
  \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize Learning from Language (Psych 711) -- Fall 2020}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}



\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}


\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={Learning from Language (Psych 711)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}





\usepackage{setspace}

\title{Learning from Language (Psych 711)}
\author{Gary Lupyan}
\date{Fall 2020}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}


	\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:lupyan@wisc.edu}{\nolinkurl{lupyan@wisc.edu}}} & Web: \href{http://sapir.psych.wisc.edu}{\tt sapir.psych.wisc.edu}\\
Office Hours: By appt. Everyone should make use of
it.  &  Class Hours: Tue 1:00pm-3:00pm\\
Office: Psych 419  & Class Room: Psych 338\\
	&  \\
	\hline
	\end{tabular*}
	
\vspace{2mm}
	


\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

This graduate seminar will focus on the question of what kinds of
knowledge are we learning from our exposure to natural language.
Consider two thought experiments: (1) Imagine if everything humans knew,
they learned from personally doing things and from observing others do
things. (2) Now imagine if the only source of information was language:
we can talk to others, read, but not experience things for ourselves.
The actual case is that people learn from their own experiences, from
observing others, and also from language in its various forms. This
brings us to the question: What aspects of semantic knowledge, if any,
do we learn exclusively from language? Which semantic domains are
especially impacted by our experiences with language? What kind of
information is especially well-represented in language, and what kind if
absent? Do some languages ``teach'' their speakers things that other
languages don't?

\hypertarget{course-learning-outcomes}{%
\section{Course Learning Outcomes}\label{course-learning-outcomes}}

Students will\ldots{}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  become familiar with a diverse literature linking language, cognition,
  and perception
\item
  be able to think critically about correlational vs.~causal claims
\item
  understand the basics of word embedding models and the core principles
  of natural language processing
\item
  design new experiment to test hypotheses about relationships between
  language and learning
\end{enumerate}

\hypertarget{expectations}{%
\section{Expectations}\label{expectations}}

Students are expected to read the 2-5 readings assigned for each class.
I expect students to critically engage with each reading. Be on the
lookout for ideas that challenge your intuitions, and that provoke you
into thinking differently. To help you engage with the readings, each
student will be randomly assigned to a group of 3-4 for each week. After
reading the papers individually, the group should get together to
discuss the readings and -- working together -- fill out a
\emph{Response Sheet} (see
\href{https://docs.google.com/document/d/1N3eQQd40xufCTC0irJMPP7barnsBlyDQFh5fp9LLJpM/edit?usp=sharing}{Template}.
Each group should upload the completed template to Canvas by 8pm the day
before class. I will grade each response sheet on a 1-3 scale
(\checkmark-, \checkmark, \checkmark+) and will use it to organize the
discussion for the following class. Please note that some weeks have
more/longer readings than other weeks. Plan your schedule accordingly.
Final projects will also be completed in groups. Each group has the
option of choosing to write a grant proposal, a review paper, or an
empirical paper using online data collection, corpus analysis, or
simulations.

\hypertarget{how-credit-hours-are-met-by-the-course}{%
\section{How credit hours are met by the
course}\label{how-credit-hours-are-met-by-the-course}}

(Times are estimates)

\begin{itemize}
\tightlist
\item
  28 hrs class-time
\item
  50 hrs reading
\item
  10 hrs weekly assignments
\item
  30 hrs final assignment\\
  = 118 hrs total
\end{itemize}

\hypertarget{grading-policy}{%
\subsection{Grading Policy}\label{grading-policy}}

\begin{itemize}
\tightlist
\item
  \textbf{40\%} Attendance / in-class participation
\item
  \textbf{25\%} Reading responses
\item
  \textbf{35\%} Final assignment
\end{itemize}

\hypertarget{class-schedule1}{%
\section[Class Schedule]{\texorpdfstring{Class
Schedule\footnote{As this is the first time this class is being offered,
  the schedule is subject to being revised.}}{Class Schedule}}\label{class-schedule1}}

The order in which the readings are listed is the recommended reading
order.

\hypertarget{week-01-tue-0908}{%
\section{Week 01, Tue, 09/08}\label{week-01-tue-0908}}

\hypertarget{introduction.-human-evolution-and-the-cultural-niche}{%
\subsubsection{Introduction. Human evolution and the cultural
niche}\label{introduction.-human-evolution-and-the-cultural-niche}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} (Boyd et al., 2011; Pagel \& Mace, 2004)
\end{itemize}

\hypertarget{week-02-tue-0915}{%
\section{Week 02, Tue, 09/15}\label{week-02-tue-0915}}

\hypertarget{varieties-of-semantic-and-conceptual-knowledge-and-its-connection-to-language}{%
\subsubsection{Varieties of semantic and conceptual knowledge and its
connection to
language}\label{varieties-of-semantic-and-conceptual-knowledge-and-its-connection-to-language}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Yee et al. (2018); Bedny \& Saxe (2012); Levinson
  (1997); Lupyan \& Bergen (2016)
\end{itemize}

\hypertarget{week-03-tue-0922}{%
\section{Week 03, Tue, 09/22}\label{week-03-tue-0922}}

\hypertarget{the-naming-ceremony-word-learning-in-weird-and-non-weird-contexts}{%
\subsubsection{The naming ceremony; word learning in WEIRD and non-WEIRD
contexts}\label{the-naming-ceremony-word-learning-in-weird-and-non-weird-contexts}}

(Please note the heavier reading load for this week)

\textbf{Special guest} - Elika Bergelson

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Waxman (1999); Bergelson \& Aslin (2017); Bergelson
  et al. (2019); Cristia et al. (2019); Brown \& Casillas (2018)
\end{itemize}

\hypertarget{week-04-tue-0929}{%
\section{Week 04, Tue, 09/29}\label{week-04-tue-0929}}

\hypertarget{analogical-and-relational-reasoning}{%
\subsubsection{Analogical and relational
reasoning}\label{analogical-and-relational-reasoning}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Hofstadter (2001); Gentner \& Boroditsky (2001);
  Loewenstein \& Gentner (2005); Gentner et al. (2013)
\end{itemize}

\hypertarget{week-05-tue-1006}{%
\section{Week 05, Tue, 10/06}\label{week-05-tue-1006}}

\hypertarget{education-literacy-language-and-intelligence.}{%
\subsubsection{Education, literacy, language, and
intelligence.}\label{education-literacy-language-and-intelligence.}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Cole (2005); Stanovich \& Cunningham (1992);
  Ritchie et al. (2015)
\end{itemize}

\hypertarget{week-06-tue-1013}{%
\section{Week 06, Tue, 10/13}\label{week-06-tue-1013}}

\hypertarget{learning-from-generics}{%
\subsubsection{Learning from generics}\label{learning-from-generics}}

(Please note the heavier reading load for this week)

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Haward et al. (2018); Hollander et al. (2009);
  Rhodes et al. (2012); Horowitz \& Frank (2016); Leslie (2014)
\end{itemize}

\hypertarget{week-07-tue-1020}{%
\section{Week 07, Tue, 10/20}\label{week-07-tue-1020}}

\hypertarget{language-and-and-the-reading-of-minds}{%
\subsubsection{Language and and the reading of
minds}\label{language-and-and-the-reading-of-minds}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} (Gagne \& Coppola, 2017; Heyes \& Frith, 2014;
  Samuel et al., 2019)
\end{itemize}

\hypertarget{week-08-tue-1027}{%
\section{Week 08, Tue, 10/27}\label{week-08-tue-1027}}

\hypertarget{distributional-semantics-1-core-principles-and-controversies}{%
\subsubsection{Distributional Semantics 1: Core Principles and
controversies}\label{distributional-semantics-1-core-principles-and-controversies}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Elman (2004); Boleda (2020); Günther et al. (2019);
  Bender \& Koller (2020)
\end{itemize}

\hypertarget{week-09-tue-1103}{%
\section{Week 09, Tue, 11/03}\label{week-09-tue-1103}}

\hypertarget{distributional-semantics-implications-for-learning}{%
\subsubsection{Distributional Semantics: Implications for
learning}\label{distributional-semantics-implications-for-learning}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} Lupyan \& Lewis (2017); Kim et al. (2019); Lewis et
  al. (2019); Grand et al. (2018); Lewis \& Lupyan (2020)
\end{itemize}

\hypertarget{week-10-tue-1110}{%
\section{Week 10, Tue, 11/10}\label{week-10-tue-1110}}

\hypertarget{language-and-emotions}{%
\subsubsection{Language and emotions}\label{language-and-emotions}}

\textbf{Special guest} - Kristen Lindquist

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} (Doyle \& Lindquist, 2017; Jackson et al., 2019;
  Lindquist et al., 2015)
\end{itemize}

\hypertarget{week-11-tue-1117}{%
\section{Week 11, Tue, 11/17}\label{week-11-tue-1117}}

\hypertarget{perception-1-top-down-effects-of-language-on-perception}{%
\subsubsection{Perception 1: Top-down effects (of language) on
perception}\label{perception-1-top-down-effects-of-language-on-perception}}

\textbf{Special guest} - Andy Clark

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} ; Lupyan \& Clark (2015); Samaha et al. (2018);
  Lupyan et al. (n.d.);
\end{itemize}

\hypertarget{week-12-tue-1124}{%
\section{Week 12, Tue, 11/24}\label{week-12-tue-1124}}

\hypertarget{perception-2-language-and-olfaction}{%
\subsubsection{Perception 2: Language and
olfaction}\label{perception-2-language-and-olfaction}}

\begin{itemize}
\tightlist
\item
  \textbf{Readings:} A. Majid et al. (2018); Majid \& Burenhult (2014);
  Asifa Majid et al. (2018); Olofsson \& Wilson (2018); Asifa Majid \&
  Kruspe (2018)
\end{itemize}

\hypertarget{week-13-tue-1201}{%
\section{Week 13, Tue, 12/01}\label{week-13-tue-1201}}

\hypertarget{writing-workshop}{%
\subsubsection{Writing workshop}\label{writing-workshop}}

\hypertarget{workshopping-you-group-papers.-details-tba.}{%
\subsubsection{Workshopping you group papers. Details
TBA.}\label{workshopping-you-group-papers.-details-tba.}}

\hypertarget{week-14-tue-1208}{%
\section{Week 14, Tue, 12/08}\label{week-14-tue-1208}}

\hypertarget{final-presentations}{%
\subsubsection{Final presentations}\label{final-presentations}}

\hypertarget{group-paper-presentations-17-min-presentations-10-min-qa.}{%
\subsubsection{Group paper presentations {[}17 min presentations + 10
min
Q\&A{]}.}\label{group-paper-presentations-17-min-presentations-10-min-qa.}}

\newpage

\hypertarget{students-rules-rights-responsibilities}{%
\section{\texorpdfstring{STUDENTS'
\href{https://guide.wisc.edu/graduate/}{RULES, RIGHTS \&
RESPONSIBILITIES}}{STUDENTS' RULES, RIGHTS \& RESPONSIBILITIES}}\label{students-rules-rights-responsibilities}}

During the global COVID-19 pandemic, we must prioritize our collective
health and safety to keep ourselves, our campus, and our community safe.
As a university community, we must work together to prevent the spread
of the virus and to promote the collective health and welfare of our
campus and surrounding community.

\hypertarget{uw-madison-badger-pledge}{%
\section{\texorpdfstring{UW-MADISON
\href{https://smartrestart.wisc.edu/badgerpledge/}{BADGER
PLEDGE}}{UW-MADISON BADGER PLEDGE}}\label{uw-madison-badger-pledge}}

\hypertarget{uw-madison-face-covering-guidelines}{%
\section{\texorpdfstring{UW-MADISON
\href{https://d1cjb8q1w2lzm7.cloudfront.net/wp-content/uploads/sites/22/2020/06/Cloth-face-cover-guidance-06-22-20-final.pdf}{FACE
COVERING
GUIDELINES}}{UW-MADISON FACE COVERING GUIDELINES}}\label{uw-madison-face-covering-guidelines}}

While on campus all employees and students are required to wear
\href{https://www.cdc.gov/coronavirus/2019-ncov/prevent-getting-sick/how-to-wear-cloth-face-coverings.html}{appropriate
and properly fitting face coverings} while present in any campus
building unless working alone in a laboratory or office space.

\hypertarget{face-coverings-during-in-person-instruction-statement-covid-19}{%
\subsection{Face Coverings During In-person Instruction Statement
(COVID-19)}\label{face-coverings-during-in-person-instruction-statement-covid-19}}

Individuals are expected to wear a face covering while inside any
university building. Face coverings must be
\href{https://www.cdc.gov/coronavirus/2019-ncov/prevent-getting-sick/how-to-wear-cloth-face-coverings.html}{worn
correctly} (i.e., covering both your mouth and nose) in the building if
you are attending class in person. If any student is unable to wear a
face-covering, an accommodation may be provided due to disability,
medical condition, or other legitimate reason.

Students with disabilities or medical conditions who are unable to wear
a face covering should contact the
\href{https://mcburney.wisc.edu/}{McBurney Disability Resource Center}
or their Access Consultant if they are already affiliated. Students
requesting an accommodation unrelated to disability or medical
condition, should contact the Dean of Students Office.

Students who choose not to wear a face covering may not attend in-person
classes, unless they are approved for an accommodation or exemption. All
other students not wearing a face covering will be asked to put one on
or leave the classroom. Students who refuse to wear face coverings
appropriately or adhere to other stated requirements will be reported to
the \href{https://conduct.students.wisc.edu/}{Office of Student Conduct
and Community Standards} and will not be allowed to return to the
classroom until they agree to comply with the face covering policy. An
instructor may cancel or suspend a course in-person meeting if a person
is in the classroom without an approved face covering in position over
their nose and mouth and refuses to immediately comply.

\hypertarget{quarantine-or-isolation-due-to-covid-19}{%
\section{QUARANTINE OR ISOLATION DUE TO
COVID-19}\label{quarantine-or-isolation-due-to-covid-19}}

Student should continually monitor themselves for COVID-19
\href{https://healthscreen.wisc.edu/}{symptoms} and get
\href{https://www.uhs.wisc.edu/medical/testing/}{tested} for the virus
if they have symptoms or have been in close contact with someone with
COVID-19. Student should reach out to instructors as soon as possible if
they become ill or need to isolate or quarantine, in order to make
alternate plans for how to proceed with the course. Students are
strongly encouraged to communicate with their instructor concerning
their illness and the anticipated extent of their absence from the
course (either in-person or remote). The instructor will work with the
student to provide alternative ways to complete the course work.

\hypertarget{course-evaluations}{%
\section{COURSE EVALUATIONS}\label{course-evaluations}}

Indicate how students can evaluate the course. For example: Students
will be provided with an opportunity to evaluate this course and your
learning experience. Student participation is an integral component of
this course, and your feedback is important to me. I strongly encourage
you to participate in the course evaluation.

\hypertarget{digital-course-evaluation-aefis}{%
\subsection{Digital Course Evaluation
(AEFIS)}\label{digital-course-evaluation-aefis}}

UW-Madison now uses an online course evaluation survey tool,
\href{https://assessment.provost.wisc.edu/course-evaluation-surveys/}{AEFIS}.
In most instances, you will receive an official email two weeks prior to
the end of the semester when your course evaluation is available. You
will receive a link to log into the course evaluation with your NetID
where you can complete the evaluation and submit it, anonymously. Your
participation is an integral component of this course, and your feedback
is important to me. I strongly encourage you to participate in the
course evaluation.

ACADEMIC CALENDAR \& RELIGIOUS OBSERVANCES

• See:
\url{https://secfac.wisc.edu/academic-calendar/\#religious-observances}

\hypertarget{ethics-of-being-a-student-in-the-department-of-psychology}{%
\section{Ethics of Being a Student in the Department of
Psychology}\label{ethics-of-being-a-student-in-the-department-of-psychology}}

The members of the faculty of the Department of Psychology at UW-Madison
uphold the highest ethical standards of teaching and research. They
expect their students to uphold the same standards of ethical conduct.
By registering for this course, you are implicitly agreeing to conduct
yourself with the utmost integrity throughout the semester.

In the Department of Psychology, acts of academic misconduct are taken
very seriously. Such acts diminish the educational experience for all
involved -- students who commit the acts, classmates who would never
consider engaging in such behaviors, and instructors. Academic
misconduct includes, but is not limited to, cheating on assignments and
exams, stealing exams, sabotaging the work of classmates, submitting
fraudulent data, plagiarizing the work of classmates or published and/or
online sources, acquiring previously written papers and submitting them
(altered or unaltered) for course assignments, collaborating with
classmates when such collaboration is not authorized, and assisting
fellow students in acts of misconduct. Students who have knowledge that
classmates have engaged in academic misconduct should report this to the
instructor.

\hypertarget{academic-integrity}{%
\section{Academic Integrity}\label{academic-integrity}}

By enrolling in this course, each student assumes the responsibilities
of an active participant in UW-Madison's community of scholars in which
everyone's academic work and behavior are held to the highest academic
integrity standards. Academic misconduct compromises the integrity of
the university. Cheating, fabrication, plagiarism, unauthorized
collaboration, and helping others commit these acts are examples of
academic misconduct, which can result in disciplinary action. This
includes but is not limited to failure on the assignment/course,
disciplinary probation, or suspension. Substantial or repeated cases of
misconduct will be forwarded to the Office of Student Conduct \&
Community Standards for additional review. For more information, refer
to studentconduct.wiscweb.wisc.edu/academic-integrity/.

\hypertarget{accommodations-policy}{%
\section{Accommodations Policy:}\label{accommodations-policy}}

\emph{McBurney Disability Resource Center syllabus statement:} ``The
University of Wisconsin-Madison supports the right of all enrolled
students to a full and equal educational opportunity. The Americans with
Disabilities Act (ADA), Wisconsin State Statute (36.12), and UW-Madison
policy (Faculty Document 1071) require that students with disabilities
be reasonably accommodated in instruction and campus life. Reasonable
accommodations for students with disabilities is a shared faculty and
student responsibility. Students are expected to inform faculty {[}me{]}
of their need for instructional accommodations by the end of the third
week of the semester, or as soon as possible after a disability has been
incurred or recognized. Faculty {[}I{]}, will work either directly with
the student {[}you{]} or in coordination with the McBurney Center to
identify and provide reasonable instructional accommodations. Disability
information, including instructional accommodations as part of a
student's educational record, is confidential and protected under
FERPA.''
\url{http://mcburney.wisc.edu/facstaffother/faculty/syllabus.php}

\_UW-Madison students who have experienced sexual misconduct (which can
include sexual harassment, sexual assault, dating violence and/or
stalking) also have the right to request academic accommodations. This
right is afforded them under Federal legislation (Title IX). Information
about services and resources (including information about how to request
accommodations) is available through Survivor Services, a part of
University Health Services:
\url{https://www.uhs.wisc.edu/survivor-services/_}

\hypertarget{diversity-and-inclusion}{%
\section{Diversity and Inclusion}\label{diversity-and-inclusion}}

\emph{Institutional statement on diversity:} ``Diversity is a source of
strength, creativity, and innovation for UW-Madison. We value the
contributions of each person and respect the profound ways their
identity, culture, background, experience, status, abilities, and
opinion enrich the university community. We commit ourselves to the
pursuit of excellence in teaching, research, outreach, and diversity as
inextricably linked goals.

The University of Wisconsin-Madison fulfills its public mission by
creating a welcoming and inclusive community for people from every
background -- people who as students, faculty, and staff serve Wisconsin
and the world.'' \url{https://diversity.wisc.edu/}

\hypertarget{complaints}{%
\section{Complaints}\label{complaints}}

Occasionally, a student may have a complaint about a TA or course
instructor. If that happens, you should feel free to discuss the matter
directly with the TA or instructor. If the complaint is about the TA and
you do not feel comfortable discussing it with him or her, you should
discuss it with the course instructor. Complaints about mistakes in
grading should be resolved with the TA and/or instructor in the great
majority of cases. If the complaint is about the instructor (other than
ordinary grading questions) and you do not feel comfortable discussing
it with him or her, make an appointment to speak to the Associate Chair
for Graduate Studies, Professor Kristin Shutts,
\href{mailto:kshutts@wisc.edu}{\nolinkurl{kshutts@wisc.edu}}.

If your complaint concerns sexual harassment, you may also take your
complaint to Dr.~Linnea Burk, Clinical Associate Professor and Director,
Psychology Research and Training Clinic, Room 315 Psychology (262-9079;
\href{mailto:burk@wisc.edu}{\nolinkurl{burk@wisc.edu}}).

If you have concerns about climate or bias in this class, or if you wish
to report an incident of bias or hate that has occurred in class, you
may contact the Chair of the Department, Professor Craig Berridge
(\href{mailto:berridge@wisc.edu}{\nolinkurl{berridge@wisc.edu}}) or the
Chair of the Psychology Department Climate \& Diversity Committee,
Professor Catherine Marler
(\href{mailto:catherine.marler@wisc.edu}{\nolinkurl{catherine.marler@wisc.edu}}).
You may also use the University's bias incident reporting system, which
you can reach at the following link:
\url{https://doso.students.wisc.edu/services/bias-reporting-process/}.

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-bedny_insights_2012}{}%
Bedny, M., \& Saxe, R. (2012). Insights into the origins of knowledge
from the cognitive neuroscience of blindness. \emph{Cognitive
Neuropsychology}, \emph{29}(1-2), 56--84.
\url{https://doi.org/10.1080/02643294.2012.713342}

\leavevmode\hypertarget{ref-bender_climbing_2020}{}%
Bender, E. M., \& Koller, A. (2020). Climbing towards NLU: On Meaning,
Form, and Understanding in the Age of Data. \emph{Proceedings of the
58th Annual Meeting of the Association for Computational Linguistics},
5185--5198. \url{https://doi.org/10.18653/v1/2020.acl-main.463}

\leavevmode\hypertarget{ref-bergelson_nature_2017}{}%
Bergelson, E., \& Aslin, R. N. (2017). Nature and origins of the lexicon
in 6-mo-olds. \emph{Proceedings of the National Academy of Sciences},
\emph{114}(49), 12916--12921.
\url{https://doi.org/10.1073/pnas.1712966114}

\leavevmode\hypertarget{ref-bergelson_what_2019}{}%
Bergelson, E., Casillas, M., Soderstrom, M., Seidl, A., Warlaumont, A.
S., \& Amatuni, A. (2019). What Do North American Babies Hear? A
large-scale cross-corpus analysis. \emph{Developmental Science},
\emph{22}(1), e12724. \url{https://doi.org/10.1111/desc.12724}

\leavevmode\hypertarget{ref-boleda_distributional_2020}{}%
Boleda, G. (2020). Distributional Semantics and Linguistic Theory.
\emph{Annual Review of Linguistics}, \emph{Accepted}.
\url{https://doi.org/10.1146/annurev-linguistics-011619-030303}

\leavevmode\hypertarget{ref-boyd_cultural_2011}{}%
Boyd, R., Richerson, P. J., \& Henrich, J. (2011). The cultural niche:
Why social learning is essential for human adaptation. \emph{Proceedings
of the National Academy of Sciences}, \emph{108}(Supplement 2),
10918--10925. \url{https://doi.org/10.1073/pnas.1100290108}

\leavevmode\hypertarget{ref-brown_childrearing_2018}{}%
Brown, P., \& Casillas, M. (2018). Childrearing through social
interaction on Rossel Island, PNG. In A. J. Fentiman \& M. Goody (Eds.),
\emph{Esther Goody revisited: Exploring the legacy of an original
inter-disciplinarian}. Berghahn.
\url{https://pure.mpg.de/pubman/faces/ViewItemFullPage.jsp?itemId=item_2621562_5}

\leavevmode\hypertarget{ref-cole_cross-cultural_2005}{}%
Cole, M. (2005). Cross-cultural and historical perspectives on the
developmental consequences of education. \emph{Human Development},
\emph{48}(4), 195--216.

\leavevmode\hypertarget{ref-cristia_child-directed_2019}{}%
Cristia, A., Dupoux, E., Gurven, M., \& Stieglitz, J. (2019).
Child-Directed Speech Is Infrequent in a Forager-Farmer Population: A
Time Allocation Study. \emph{Child Development}, \emph{90}(3), 759--773.
\url{https://doi.org/10.1111/cdev.12974}

\leavevmode\hypertarget{ref-doyle_language_2017}{}%
Doyle, C. M., \& Lindquist, K. A. (2017). Language and emotion:
Hypotheses on the constructed nature of emotion perception. In J. M.
Fernández-Dols \& J. A. Russell (Eds.), \emph{Oxford series in social
cognition and social neuroscience. The science of facial expression}
(pp. 415--432). Oxford University Press.

\leavevmode\hypertarget{ref-elman_alternative_2004}{}%
Elman, J. L. (2004). An alternative view of the mental lexicon.
\emph{Trends in Cognitive Sciences}, \emph{8}(7), 301--306.
\url{https://doi.org/10.1016/j.tics.2004.05.003}

\leavevmode\hypertarget{ref-gagne_visible_2017}{}%
Gagne, D. L., \& Coppola, M. (2017). Visible Social Interactions Do Not
Support the Development of False Belief Understanding in the Absence of
Linguistic Input: Evidence from Deaf Adult Homesigners. \emph{Frontiers
in Psychology}, \emph{8}. \url{https://doi.org/10.3389/fpsyg.2017.00837}

\leavevmode\hypertarget{ref-gentner_individuation_2001}{}%
Gentner, D., \& Boroditsky, L. (2001). Individuation, relational
relativity and early word learning. In M. Bowerman \& S. C. Levinson
(Eds.), \emph{Language acquisition and conceptual development}.
Cambridge University Press.

\leavevmode\hypertarget{ref-gentner_spatial_2013-1}{}%
Gentner, D., Özyürek, A., Gürcanli, Ö., \& Goldin-Meadow, S. (2013).
Spatial language facilitates spatial cognition: Evidence from children
who lack language input. \emph{Cognition}, \emph{127}(3), 318--330.
\url{https://doi.org/10.1016/j.cognition.2013.01.003}

\leavevmode\hypertarget{ref-grand_semantic_2018}{}%
Grand, G., Blank, I. A., Pereira, F., \& Fedorenko, E. (2018). Semantic
projection: Recovering human knowledge of multiple, distinct object
features from word embeddings. \emph{arXiv:1802.01241 {[}Cs{]}}.
\url{http://arxiv.org/abs/1802.01241}

\leavevmode\hypertarget{ref-gunther_vector-space_2019}{}%
Günther, F., Rinaldi, L., \& Marelli, M. (2019). Vector-Space Models of
Semantic Representation From a Cognitive Perspective: A Discussion of
Common Misconceptions. \emph{Perspectives on Psychological Science},
\emph{14}(6), 1006--1033. \url{https://doi.org/10.1177/1745691619861372}

\leavevmode\hypertarget{ref-haward_development_2018}{}%
Haward, P., Wagner, L., Carey, S., \& Prasada, S. (2018). The
development of principled connections and kind representations.
\emph{Cognition}, \emph{176}, 255--268.
\url{https://doi.org/10.1016/j.cognition.2018.02.001}

\leavevmode\hypertarget{ref-heyes_cultural_2014}{}%
Heyes, C. M., \& Frith, C. D. (2014). The cultural evolution of mind
reading. \emph{Science}, \emph{344}(6190).
\url{https://doi.org/10.1126/science.1243091}

\leavevmode\hypertarget{ref-hofstadter_analogy_2001}{}%
Hofstadter, D. R. (2001). Analogy as the Core of Cognition. In D.
Gentner, K. J. Holyoak, \& B. N. Kokinov (Eds.), \emph{The Analogical
Mind: Perspectives from Cognitive Science} (pp. 499--538). The MIT
Press/Bradford Book.
\url{http://prelectur.stanford.edu/lecturers/hofstadter/analogy.html}

\leavevmode\hypertarget{ref-hollander_generic_2009}{}%
Hollander, M. A., Gelman, S. A., \& Raman, L. (2009). Generic language
and judgements about category membership: Can generics highlight
properties as central? \emph{Language and Cognitive Processes},
\emph{24}(4), 481--505. \url{https://doi.org/10.1080/01690960802223485}

\leavevmode\hypertarget{ref-horowitz_childrens_2016}{}%
Horowitz, A. C., \& Frank, M. C. (2016). Children's Pragmatic Inferences
as a Route for Learning About the World. \emph{Child Development},
\emph{87}(3), 807--819. \url{https://doi.org/10.1111/cdev.12527}

\leavevmode\hypertarget{ref-jackson_emotion_2019}{}%
Jackson, J. C., Watts, J., Henry, T. R., List, J.-M., Forkel, R., Mucha,
P. J., Greenhill, S. J., Gray, R. D., \& Lindquist, K. A. (2019).
Emotion semantics show both cultural variation and universal structure.
\emph{Science}, \emph{366}(6472), 1517--1522.
\url{https://doi.org/10.1126/science.aaw8160}

\leavevmode\hypertarget{ref-kim_knowledge_2019}{}%
Kim, J. S., Elli, G. V., \& Bedny, M. (2019). Knowledge of animal
appearance among sighted and blind adults. \emph{Proceedings of the
National Academy of Sciences}, \emph{116}(23), 11213--11222.
\url{https://doi.org/10.1073/pnas.1900952116}

\leavevmode\hypertarget{ref-leslie_carving_2014}{}%
Leslie, S.-J. (2014). Carving up the Social World with Generics. In J.
Knobe, T. Lombrozo, \& S. Nichols (Eds.), \emph{Carving Up the Social
World with Generics*} (pp. 208--231). Oxford University Press.
\url{https://oxford.universitypressscholarship.com/view/10.1093/acprof:oso/9780198718765.001.0001/acprof-9780198718765-chapter-9}

\leavevmode\hypertarget{ref-levinson_outer_1997}{}%
Levinson, S. C. (1997). From outer to inner space: Linguistic categories
and non-linguistic thinking. In J. Nuyts \& E. Pederson (Eds.),
\emph{Language and conceptualization} (pp. 13--45). Cambridge University
Press.

\leavevmode\hypertarget{ref-lewis_gender_2020}{}%
Lewis, M., \& Lupyan, G. (2020). Gender stereotypes are reflected in the
distributional structure of 25 languages. \emph{Nature Human Behaviour},
1--8. \url{https://doi.org/10.1038/s41562-020-0918-6}

\leavevmode\hypertarget{ref-lewis_distributional_2019}{}%
Lewis, M., Zettersten, M., \& Lupyan, G. (2019). Distributional
semantics as a source of visual knowledge. \emph{Proceedings of the
National Academy of Sciences}, \emph{116}(39), 19237--19238.
\url{https://doi.org/10.1073/pnas.1910148116}

\leavevmode\hypertarget{ref-lindquist_role_2015}{}%
Lindquist, K. A., MacCormack, J. K., \& Shablack, H. (2015). The role of
language in emotion: Predictions from psychological constructionism.
\emph{Frontiers in Psychology}, \emph{6}.
\url{https://doi.org/10.3389/fpsyg.2015.00444}

\leavevmode\hypertarget{ref-loewenstein_relational_2005}{}%
Loewenstein, J., \& Gentner, D. (2005). Relational language and the
development of relational mapping. \emph{Cognitive Psychology},
\emph{50}(4), 315--353.
\url{https://doi.org/10.1016/j.cogpsych.2004.09.004}

\leavevmode\hypertarget{ref-lupyan_effects_nodate}{}%
Lupyan, G., Abdel Rahman, R., Boroditsky, L., \& Clark, A. (n.d.).
Effects of Language on Visual Perception. \emph{Trends in Cognitive
Science}. \url{https://doi.org/10.31234/osf.io/pztmc}

\leavevmode\hypertarget{ref-lupyan_how_2016}{}%
Lupyan, G., \& Bergen, B. (2016). How Language Programs the Mind.
\emph{Topics in Cognitive Science}, \emph{8}(2), 408--424.
\url{https://doi.org/10.1111/tops.12155}

\leavevmode\hypertarget{ref-lupyan_words_2015}{}%
Lupyan, G., \& Clark, A. (2015). Words and the World: Predictive coding
and the language-perception-cognition interface. \emph{Current
Directions in Psychological Science}, \emph{24}(4), 279--284.
\url{https://doi.org/10.1177/0963721415570732}

\leavevmode\hypertarget{ref-lupyan_words-as-mappings_2017}{}%
Lupyan, G., \& Lewis, M. (2017). From words-as-mappings to
words-as-cues: The role of language in semantic knowledge.
\emph{Language, Cognition and Neuroscience}, \emph{34}(10), 1319--1337.
\url{https://doi.org/10.1080/23273798.2017.1404114}

\leavevmode\hypertarget{ref-majid_odors_2014}{}%
Majid, A., \& Burenhult, N. (2014). Odors are expressible in language,
as long as you speak the right language. \emph{Cognition},
\emph{130}(2), 266--270.
\url{https://doi.org/10.1016/j.cognition.2013.11.004}

\leavevmode\hypertarget{ref-majid_olfactory_2018}{}%
Majid, A., Burenhult, N., Stensmyr, M., de Valk, J., \& Hansson, B. S.
(2018). Olfactory language and abstraction across cultures.
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, \emph{373}(1752), 20170139.
\url{https://doi.org/10.1098/rstb.2017.0139}

\leavevmode\hypertarget{ref-majid_hunter-gatherer_2018}{}%
Majid, A., \& Kruspe, N. (2018). Hunter-Gatherer Olfaction Is Special.
\emph{Current Biology}, \emph{28}(3), 409--413.e2.
\url{https://doi.org/10.1016/j.cub.2017.12.014}

\leavevmode\hypertarget{ref-majid_differential_2018}{}%
Majid, A., Roberts, S. G., Cilissen, L., Emmorey, K., Nicodemus, B.,
O'Grady, L., Woll, B., LeLan, B., Sousa, H. de, Cansler, B. L., Shayan,
S., Vos, C. de, Senft, G., Enfield, N. J., Razak, R. A., Fedden, S.,
Tufvesson, S., Dingemanse, M., Ozturk, O., \ldots{} Levinson, S. C.
(2018). Differential coding of perception in the world's languages.
\emph{Proceedings of the National Academy of Sciences}, \emph{115}(45),
11369--11376. \url{https://doi.org/10.1073/pnas.1720419115}

\leavevmode\hypertarget{ref-olofsson_human_2018}{}%
Olofsson, J. K., \& Wilson, D. A. (2018). Human Olfaction: It Takes Two
Villages. \emph{Current Biology}, \emph{28}(3), R108--R110.
\url{https://doi.org/10.1016/j.cub.2017.12.016}

\leavevmode\hypertarget{ref-pagel_cultural_2004}{}%
Pagel, M., \& Mace, R. (2004). The cultural wealth of nations.
\emph{Nature}, \emph{428}(6980), 275--278.
\url{https://doi.org/10.1038/428275a}

\leavevmode\hypertarget{ref-rhodes_cultural_2012}{}%
Rhodes, M., Leslie, S.-J., \& Tworek, C. M. (2012). Cultural
transmission of social essentialism. \emph{Proceedings of the National
Academy of Sciences}, \emph{109}(34), 13526--13531.
\url{https://doi.org/10.1073/pnas.1208951109}

\leavevmode\hypertarget{ref-ritchie_does_2015}{}%
Ritchie, S. J., Bates, T. C., \& Plomin, R. (2015). Does Learning to
Read Improve Intelligence? A Longitudinal Multivariate Analysis in
Identical Twins From Age 7 to 16. \emph{Child Development},
\emph{86}(1), 23--36. \url{https://doi.org/10.1111/cdev.12272}

\leavevmode\hypertarget{ref-samaha_effects_2018}{}%
Samaha, J., Boutonnet, B., Postle, B. R., \& Lupyan, G. (2018). Effects
of meaningfulness on perception: Alpha-band oscillations carry
perceptual expectations and influence early visual responses.
\emph{Scientific Reports}, \emph{8}(1), 6606.
\url{https://doi.org/10.1038/s41598-018-25093-5}

\leavevmode\hypertarget{ref-samuel_is_2019}{}%
Samuel, S., Durdevic, K., Legg, E. W., Lurz, R., \& Clayton, N. S.
(2019). Is Language Required to Represent Others' Mental States?
Evidence From Beliefs and Other Representations. \emph{Cognitive
Science}, \emph{43}(1), e12710. \url{https://doi.org/10.1111/cogs.12710}

\leavevmode\hypertarget{ref-stanovich_studying_1992}{}%
Stanovich, K. E., \& Cunningham, A. E. (1992). Studying the consequences
of literacy within a literate society: The cognitive correlates of print
exposure. \emph{Memory \& Cognition}, \emph{20}(1), 51--68.
\url{https://doi.org/10.3758/BF03208254}

\leavevmode\hypertarget{ref-waxman_dubbing_1999}{}%
Waxman, S. R. (1999). The dubbing ceremony revisited: Object naming and
categorization in infancy and early childhood. In D. L. Medin \& S.
Atran (Eds.), \emph{Folkbiology} (pp. 233--284). MIT Press.

\leavevmode\hypertarget{ref-yee_semantic_2018}{}%
Yee, E., Jones, M. N., \& McRae, K. (2018). Semantic Memory. In J. W.
\&. S. Thompson-Schill (Ed.), \emph{The Stevens' Handbook of
Experimental Psychology and Neuroscience, Fourth Edidition} (pp.
319--356). Wiley.
\end{cslreferences}




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
