\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize PLCP: Introduction to Comparative Political
Economy -- Fall 2018}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={PLCP: Introduction to Comparative Political
Economy},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}





\usepackage{setspace}

\title{PLCP: Introduction to Comparative Political Economy}
\author{Robert Kubinec}
\date{Fall 2018}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}


	\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:rmk7xy@virginia.edu}{\nolinkurl{rmk7xy@virginia.edu}}} & Web: \href{http://www.robertkubinec.com}{\tt www.robertkubinec.com}\\
Office Hours: W 09:00-11:30 a.m.  &  Class Hours: XXX\\
Office: XXXX  & Class Room: \emph{XXX}\\
	&  \\
	\hline
	\end{tabular*}
	
\vspace{2mm}
	


\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

Comparative political economy is the study of political institutions
that control economic activity and the ramifications that these
institutions have on political outcomes, including social movements,
elections and legislatures. The discipline has a very rich history,
dating as far back as Aristotle, but it received its current form during
the 18th and 19th centuries where we will begin our course overview.
Lately, research in comparative political economy has explored social
and political phenomena not considered to be heavily affected by
economic constraints, such as media coverage, sectarianism and the rebel
group recruitment. Through this broadening of political economy, the
field has become distilled into a set of principles, called rational
choice, that can be applied to a wide set of social institutions. In
this class, we will explore the traditional study of political-economic
outcomes, including the effects of income inequality, trade, corruption
and international financial institutions (IFIs), along with a summary of
trending research in election fraud, one-party states, and civil wars.

\hypertarget{course-objectives}{%
\section{Course Objectives}\label{course-objectives}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Attain mastery of evaluation and critique of a wide range of readings
  in the discipline of political economy;
\item
  Employ the rational-choice approach in theoretical and applied
  settings through class discussion \& writing;
\item
  Engage in the scholarly process of discovery through an independent
  research project.
\end{enumerate}

\hypertarget{required-texts}{%
\section{Required Texts}\label{required-texts}}

The following two books have been purchased and are available at the
book store. I have also placed a copy of each on reserve at the library.
We will spend a week on each book as intensive deep-dive into the
arguments made by these authors and how they use political economy as a
methodology for research.

\begin{verbatim}
## No results.
\end{verbatim}

list()

\hypertarget{course-policies}{%
\section{Course Policies}\label{course-policies}}

Please use the information below as a reference for how this class will
be conducted. I would ask that you review this information before
contacting me with any questions.

\hypertarget{grading-policy}{%
\subsection{Grading Policy}\label{grading-policy}}

\begin{itemize}
\item
  \textbf{20\%} of your grade will be determined by a midterm during
  normal class hours.
\item
  \textbf{40\%} of your grade will come from a 15-20 page (graduate:
  25-30 page) paper that explores in further detail one of the research
  areas on the class syllabus. By the midterm students must have three
  hypotheses related to one of these research areas and a draft of
  available resources, which will constitute 5\% of the 40\%. I expect
  that students will use original data collection, whether quantitative
  or qualitative, to answer the questions posed.
\item
  \textbf{20\%} of your grade will be determined by your attendance and
  participation in class. I expect you to come having read the reading
  and prepared to pose at least one question or critique of the readings
  for that week.
\item
  \textbf{20\%} of your grade will come from three 2-page critical
  summaries of the reading that you must complete on three separate
  weeks of the class.
\end{itemize}

\hypertarget{attendance-policy}{%
\subsection{Attendance Policy}\label{attendance-policy}}

\hypertarget{late-arrival-of-the-professor-policy}{%
\subsection{Late Arrival of the Professor
Policy}\label{late-arrival-of-the-professor-policy}}

My current university, from what I have been told, asks professors to
have policies written into their syllabus about what students should do
if the professor is more than 15 minutes late to class. This seems like
an anachronism. I will inform students via e-mail in advance of class if
class is cancelled for the day. I will also contact our department
secretary if something happened on the way to work. Failing that, assume
the worst happened to me. I ask the students make sure that my story
gets the proper treatment on an \emph{Investigation Discovery} show. I
also ask that my story be narrated by Keith Morrison.

\hypertarget{e-mail-policy}{%
\subsection{E-mail Policy}\label{e-mail-policy}}

I am usually quick to respond to student e-mails. However, student
e-mails tend to do several things that try my patience. I have a new
policy, effective Fall 2016, that outlines why I will not respond to
certain e-mails students send. Multiple rationales follow.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The student could answer his/her own inquiry by reading the syllabus.
\item
  The student missed class for which there was no exam. I do not need to
  know the exact reason for a missed class. Students with excusable
  absences are responsible for giving me a note \emph{in hard copy} that
  documents the reason for the missed class. An e-mail is unnecessary
  unless the impromptu absence involved missing a midterm or final.
\item
  The student wants to know what topics s/he missed during a class s/he
  skipped. The answer is always ``you missed what was on the syllabus.''
\item
  The student is protesting a grade without reference to specific points
  of objection. See the policy on protesting a grade in the syllabus.
  These e-mails tend to be expressive utility on the part of the student
  and do not require a response from me. Students interested in
  improving their knowledge of material should see me during office
  hours.
\item
  The students wants to know how many classes s/he missed at some point
  during the semester. I assume the student has a better answer to that
  question than me until the end of the semester.
\item
  The student is requesting an extension on an assignment for which the
  syllabus already established the deadline. The answer is always
  ``no''.
\item
  The student is
  \href{https://www.math.uh.edu/~tomforde/GradeGrubbing.html}{``grade
  grubbing''} or asking to round up a grade. The answer is always
  ``no''.
\item
  The student is asking for an extra credit opportunity, a request that
  amounts to more grading for the professor. The answer is ``no''.
\end{enumerate}

\hypertarget{make-up-exam-policy}{%
\subsection{Make-Up Exam Policy}\label{make-up-exam-policy}}

There are \textbf{NO} make-ups for missed exams. Don't bother asking.

\hypertarget{academic-dishonesty-policy}{%
\subsection{Academic Dishonesty
Policy}\label{academic-dishonesty-policy}}

Don't cheat. Don't be that guy. Yes, you. You know exactly what I'm
talking about too.

\hypertarget{disabilities-policy}{%
\subsection{Disabilities Policy}\label{disabilities-policy}}

Federal law mandates the provision of services at the university-level
to qualified students with disabilities. Make sure to include all that
relevant information here.

\newpage

\hypertarget{class-schedule}{%
\section{Class Schedule}\label{class-schedule}}

Students must read the following before Tuesday's class session.
Important: class readings are subject to change, contingent on
mitigating circumstances and the progress we make as a class. Students
are encouraged to attend lectures and check the course website for
updates.

\hypertarget{week-01-0827---0831-syllabus-day}{%
\subsection{Week 01, 08/27 - 08/31: Syllabus
Day}\label{week-01-0827---0831-syllabus-day}}

\emph{No class Thursday (Political scientists usually have a conference
to start the semester).}

Read \emph{all} associated documents on course website.

\begin{itemize}
\tightlist
\item
  \href{http://svmiller.com/blog/2014/09/taking-good-notes/}{Taking Good
  Notes}
\item
  \href{http://svmiller.com/blog/2015/06/dos-and-donts-of-writing-for-students/}{Dos
  and Dont's of Writing for Students}
\item
  \href{http://svmiller.com/blog/2015/12/assorted-tips-students-research-papers/}{Assorted
  Tips for Students on Writing Research Papers}
\item
  \href{https://www.dropbox.com/s/apihjs7di81aqcv/svm-exam-grading-policy.pdf?dl=0}{Exam
  Grading Policy}
\item
  \href{http://svmiller.com/blog/2016/05/fun-with-attendance-grades/}{Fun
  with Attendance and Grades (i.e.~Students Should Attend Class)}
\end{itemize}

\hypertarget{week-02-0903---0907-the-first-topic-where-we-read-john-vasquez}{%
\subsection{Week 02, 09/03 - 09/07: The First Topic Where We Read John
Vasquez}\label{week-02-0903---0907-the-first-topic-where-we-read-john-vasquez}}

\begin{verbatim}
## No results.
\end{verbatim}

list()

\hypertarget{week-03-0910---0914-read-the-nos.-90-97-items-in-my-bib}{%
\subsection{Week 03, 09/10 - 09/14: Read the Nos. 90-97 Items in My
Bib}\label{week-03-0910---0914-read-the-nos.-90-97-items-in-my-bib}}

\begin{verbatim}
## Warning in `[[.BibEntry`(x, ind): subscript out of bounds
\end{verbatim}

\emph{Your ``Slow Ride'' appreciation paper is due in Thursday's class}.

\hypertarget{week-04-0917---0921-read-bib-item-no.-120}{%
\subsection{Week 04, 09/17 - 09/21: Read Bib Item
No.~120}\label{week-04-0917---0921-read-bib-item-no.-120}}

\begin{verbatim}
## Warning in `[[.BibEntry`(x, ind): subscript out of bounds
\end{verbatim}

\hypertarget{week-05-0924---0928-the-fourth-topic-with-bib-item-no.-510}{%
\subsection{Week 05, 09/24 - 09/28: The Fourth Topic with Bib Item
No.~510}\label{week-05-0924---0928-the-fourth-topic-with-bib-item-no.-510}}

\begin{verbatim}
## Warning in `[[.BibEntry`(x, ind): subscript out of bounds
\end{verbatim}

\hypertarget{week-06-1001---1005-keep}{%
\subsection{Week 06, 10/01 - 10/05:
Keep}\label{week-06-1001---1005-keep}}

\hypertarget{week-07-1008---1012-going}{%
\subsection{Week 07, 10/08 - 10/12:
Going}\label{week-07-1008---1012-going}}

\hypertarget{week-08-1015---1019-down}{%
\subsection{Week 08, 10/15 - 10/19:
Down}\label{week-08-1015---1019-down}}

\hypertarget{week-09-1022---1026-the}{%
\subsection{Week 09, 10/22 - 10/26: the}\label{week-09-1022---1026-the}}

\hypertarget{week-10-1029---1102-line}{%
\subsection{Week 10, 10/29 - 11/02:
Line}\label{week-10-1029---1102-line}}

\hypertarget{week-11-1105---1109-until}{%
\subsection{Week 11, 11/05 - 11/09:
Until}\label{week-11-1105---1109-until}}

\hypertarget{week-12-1112---1116-you}{%
\subsection{Week 12, 11/12 - 11/16: You}\label{week-12-1112---1116-you}}

\hypertarget{week-13-1119---1123-are}{%
\subsection{Week 13, 11/19 - 11/23: Are}\label{week-13-1119---1123-are}}

\hypertarget{week-14-1126---1130-done}{%
\subsection{Week 14, 11/26 - 11/30:
Done}\label{week-14-1126---1130-done}}

\hypertarget{week-15-1203---1207-with}{%
\subsection{Week 15, 12/03 - 12/07:
with}\label{week-15-1203---1207-with}}

\hypertarget{week-16-1210---1214-your}{%
\subsection{Week 16, 12/10 - 12/14:
your}\label{week-16-1210---1214-your}}

\hypertarget{week-17-1217---1221-syllabus}{%
\subsection{Week 17, 12/17 - 12/21:
Syllabus}\label{week-17-1217---1221-syllabus}}




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
